HPC--101\\Onboarding

### 2025-03-14 hpc_101/sections/00_title.tex
corrections to early slides of hpc101, addition of new members, correction to node prices.
added another team member
switch over to new presentation for new cluster
update to slides for stale information
update the slides to contain updated info.
update to slides for onboarding
update cluster stats and group info

\author{Gwen Jacobs Ph.D.,\\Sean Cleveland Ph.D., Ron Merrill Ph.D.,\\Jennifer Geis M.S., David Schanzenbach M.S.}
\institute[University of {\hawaii} -- ITS--CI] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Information Technology Services \\
{\ci} \\
University of {\hawaii} \\ % Your institution for the title page
\medskip
\textbf{\url{https://www.hawaii.edu/its/ci/}}\\
\textbf{\textit{uh-hpc-help@lists.hawaii.edu}} % Your email address
}
\date{\today} % Date, can be changed to a custom date

>>>>

\author{Acting Director: Sean Cleveland\\Adriana Comerford, Ron Merrill, David Schanzenbach}
%\author{Director: Gwen Jacobs\\Associate Director: Sean Cleveland\\Victor Goicoechea Casanueva,\\Ron Merrill, David Schanzenbach}
%\author{Director: Gwen Jacobs\\Sean Cleveland, Adriana Comerford, Jennifer Geis,\\Ron Merrill, David Schanzenbach}
\institute[University of {\hawaii} -- ITS--RCI] % Your institution as it will appear on the bottom of every slide, may be shorthand to save space
{
Information Technology Services \\
{\ci} \\
University of {\hawaii} \\ % Your institution for the title page
\medskip
\textbf{\url{https://datascience.hawaii.edu/}}\\
%\textbf{\url{https://www.hawaii.edu/its/ci/}}\\
\textbf{\textit{uh-hpc-help@lists.hawaii.edu}} % Your email address
}
\date{\today} % Date, can be changed to a custom date

### 2025-03-14 hpc_101/sections/01_intro.tex
update cluster stats and group info

              {}               & \thead{\textbf{Nodes}} & \thead{\textbf{CPU Cores}} & \thead{\textbf{Memory}} & \thead{\textbf{GPUs}} & \thead{\textbf{Home Space}} & \thead{\textbf{Scratch Space}} & \thead{\textbf{Storage for lease}} \\ 
							\midrule  \midrule %\hline
        \thead{\textbf{Total}} & 269                    & 7,501                      & 53 TB                   &  146                   & 50 GB per user                             &  800 TB                        & 2 PB              \\ %\hline
				\bottomrule
      \end{tabular}%
    }
  \end{table}
	\end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{Scratch Storage}
  \begin{enumerate}
    \item {\lustre}
      \begin{itemize}
			\item A parallel distributed file system 
      \end{itemize}
    %\item NFS
      %\begin{itemize}
			%\item A distributed file system 
      %\end{itemize}
  \end{enumerate}
~\\
  Scratch file systems on {\mana} have the following attributes:
  \begin{itemize}
	\item 800 TB and 400K file/folder (inode) quota shared by all users
  \item \textbf{Purge policy} -- 90 days based on file modify time
  \item Available on all nodes
  \item Freely available to users
  \end{itemize}

>>>>

              {}               & \thead{\textbf{Nodes}} & \thead{\textbf{CPU Cores}} & \thead{\textbf{Memory}} & \thead{\textbf{GPUs}} & \thead{\textbf{Home Space}} & \thead{\textbf{Scratch Space}} & \thead{\textbf{Storage for lease}} \\ 
							\midrule  \midrule %\hline
        \thead{\textbf{Total}} & 287                    & 8,559                      & 61 TB                   &  140                   & 50 GB per user                             &  800 TB                        & 2 PB              \\ %\hline
				\bottomrule
      \end{tabular}%
    }
  \end{table}
	\end{block}
\end{frame}

@@

\begin{frame}
  \frametitle{Scratch Storage}
  \begin{enumerate}
    \item {\lustre}
      \begin{itemize}
			\item A parallel distributed file system 
      \end{itemize}
    %\item NFS
      %\begin{itemize}
			%\item A distributed file system 
      %\end{itemize}
  \end{enumerate}
~\\
  Scratch file systems on {\mana} have the following attributes:
  \begin{itemize}
	\item 800 TB and 400M file/folder (inode) quota shared by all users
  \item \textbf{Purge policy} -- 90 days based on file modify time
  \item Available on all nodes
  \item Freely available to users
  \end{itemize}
